---
title: "EPPS 6356 Assignment 4: 48-Hour Chart Hackathon"
subtitle: "Happy Planet Index, 2025"
author:
  - name: Rose Mikame
  - name: Susan Mohammad
  - name: Chakrayuddh Kimsovanna
date: "October 2, 2026"

format:
  html:
    toc: true
    toc-title: "Contents"
    page-layout: full

execute:
  echo: false
  warning: false
  message: false
---

## Chart 1 — Variable-Width Column Chart

```{r}
#| fig-width: 8
#| fig-height: 6
#| out-width: "100%"
#| fig-align: center

source("R_codes/chart1_variable_width.R")
chart1
```

<details>
<summary>Show R code</summary>

```{r}
#| results: asis

code <- readLines("R_codes/chart1_variable_width.R")

cat(
  "```r\n",
  paste(code, collapse = "\n"),
  "\n```\n",
  sep = ""
)
```

</details>


## Chart 2 — Table with Embedded Charts

```{r}
source("R_codes/chart2_embedded_table.R")
chart2
```

<details>
<summary>Show R code</summary>

```{r}
#| results: asis

code <- readLines("R_codes/chart2_embedded_table.R")

cat(
  "```r\n",
  paste(code, collapse = "\n"),
  "\n```\n",
  sep = ""
)
```

</details>


## Chart 3 — Top and Bottom HPI Countries

```{r}
#| fig-width: 8
#| fig-height: 11
#| out-width: "100%"
#| fig-align: center

source("R_codes/chart3_bar.R")
chart3
```

<details>
<summary>Show R code</summary>

```{r}
#| results: asis

code <- readLines("R_codes/chart3_bar.R")

cat(
  "```r\n",
  paste(code, collapse = "\n"),
  "\n```\n",
  sep = ""
)
```

</details>


## Chart 4 — Ecological Footprint by Region

```{r}
#| fig-width: 8
#| fig-height: 6
#| out-width: "100%"
#| fig-align: center

source("R_codes/chart4_column.R")
chart4
```

<details>
<summary>Show R code</summary>

```{r}
#| results: asis

code <- readLines("R_codes/chart4_column.R")

cat(
  "```r\n",
  paste(code, collapse = "\n"),
  "\n```\n",
  sep = ""
)
```

</details>


## Project Files and Sources

The project repository can be found [here](https://github.com/cykimsovanna/epps6356-assignment4-hackathon). The repository contains the R scripts, dataset used, AI disclosure, session information, and other supporting project files.